
\subsection{System feature: Group Page}
\subsection{View Grouppage}
  \begin{itemize}
          \item{\textbf{Actors:} Logged in Users}
          \item{\textbf{Goals:} User will view information about a Gus group.}
          \item{\textbf{Preconditions:} User is a member of Gus and logged in.}
          \item{\textbf{Summary:} The grouppage contains all relevant information about a group, including forum information, users in the group, and status. }
	  \item{\textbf{Steps:}}
	  \begin{enumerate}
	       \item{User logs into Gus with a valid account.}
	       \item{User goes to their personal page and clicks on a group they are in OR User clicks on the Group button on the left side and selects a group.}
	       \item{User views the grouppage if they have the proper permissions.}
	  \end{enumerate}
	  \item{\textbf{Postconditions:} User is now viewing a group's grouppage.}
	  \item{\textbf{Related use cases:} View Profile }
     \end{itemize}
\subsection{Edit Grouppage}
  \begin{itemize}
          \item{\textbf{Actors:} Logged in Users}
          \item{\textbf{Goals:} User will edit a group's information.}
          \item{\textbf{Preconditions:} User is a member of Gus, logged in, and an admin of the group.}
          \item{\textbf{Summary:} The user, if an admin of the group, is able to modify a group's information, which is then saved in the database.}
	  \item{\textbf{Steps:}}
	    \begin{enumerate}
	    \item{User logs into Gus and navigates to the group's page.}
	    \item{User clicks on the ``Edit this Group'' link.}
	    \item{User modifies whatever information they want and presses the ``Submit'' button to confirm.}
	    \end{enumerate}
	  \item{\textbf{Alternatives:}}
	  \begin{itemize}
	       \item{User can click on the ``Cancel'' button to leave at any time.}
	  \end{itemize}
	  \item{\textbf{Postconditions:} If changed, the new information is added to the database.}
	  \item{\textbf{Related use cases:} View Group Page }
     \end{itemize}
\subsection{View Group File Page}
  \begin{itemize}
          \item{\textbf{Actors:} Logged in Users}
          \item{\textbf{Goals:} User will view the files of a group}
          \item{\textbf{Preconditions:} User is looged into Gus and viewing a grouppage.}
          \item{\textbf{Summary:} If the user has proper read permissions, they will see a page containing the different files of a group. Each file, if clicked on, will take the user to its relevant Doc page.}
	  \item{\textbf{Steps:}}
	  \begin{enumerate}
	       \item{User logs into Gus and navigates to a group page.}
	       \item{User clicks on the ``View Group files'' link.}
	       \item{User gains access to all Docs functionality for the group's files.}
	  \end{enumerate}
	  \item{\textbf{Alternatives:}}
	  \begin{itemize}
	       \item{User can click the ``Back'' link at any time to go back to the group page.}
	  \end{itemize}
	  \item{\textbf{Postconditions:} User can modify any information regarding the group's files.}
	  \item{\textbf{Related use cases:} Upload File, Download File, View File Online, Delete File, Change File Permissions}
     \end{itemize}
