\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\title{GusPHP}
\date{February 4th, 2011}
\begin{document}
\maketitle
\begin{center}\textbf{Minutes of the meeting of GusPHP, University of Idaho CS-384 Spring 2011} \end{center} \\ 
\\
Colby Blair - Group Leader\\ 
\\
\textbf{McClure 209 (in class), UI Campus, Moscow ID 83843} \\ 
\\
\textbf{Present}\\ 
Brett\\
Abhay\\
Zeke\\
Alex\\
Cindy\\
Colby\\
Scott\\
Tim\\
\\
\textbf{In Attendance}\\
None \\
\\
\section{Actions for consideration} \\
None \\
\\
\section{Any Other Business}
None \\
\\
\section{New Business}
Scrums are 1 week increments. Planning is complete at end of minutes. Code, Test, and Document this Scrum.\\
What will be completed in the next Scrum:\\
Everyone - \\
\begin{itemize}
  \item Finish BREADTH of your tests
  \item Start DEPTH of your tests
  \item Standardize your DB against the standard gusphp.sql DB in php/db
  \item Make sure all controllers work on your install, and your controllers work on others
\end{itemize}
\begin{itemize}
\item Cindy:
\begin{enumerate}
 \item Document inventory of MVC's.
 \item Create a VM of WAMP/LAMP/etc that works for everyone (OS's, arch's, etc)
 \item Read about PHPDoc and start helping everyone use it to document code. More?
 \item Talk with all developers, inventory functionality and bring up at next meeting how to centralize functions
 \item After talking with all dev'ers, create Red/Green Light tests to their existing test functions.
\end{enumerate}
\item Chaylo:
\begin{enumerate}
 \item Not present, please meet with us Chaylo! Also see Tim section, he is assisting you.
\end{enumerate}
\item Zeke:
\begin{enumerate}
 \item finish linking calendar to db
 \item finish week and day views of calendar
 \item start Security Controller, stub out and finish basic functionality
\end{enumerate}
\item Abhay:
\begin{enumerate}
 \item see last week, will move on to new controller Monday.
\end{enumerate}
\item Alex:
\begin{enumerate}
 \item finish file display function/views
 \item finish delete file function/views
 \item start edit file function/views
 \item talk with other user table dev'ers in gusphp and standardize / include user permission functionality
\end{enumerate}
\item Scott:
\begin{enumerate}
 \item work on (finish?) search controller?
 \item have usable Google custom search alternative until then
\end{enumerate}
\item Brett:
\begin{enumerate}
 \item finish user integration with user/group page controllers
\end{enumerate}
\item Leah:
\begin{enumerate}
 \item assist Cindy
\end{enumerate}
\item Tim:
\begin{enumerate}
 \item assist with forum controller
 \item finish add/delete boards
 \item finish add/delete threads (children of boards)
 \item potential real web server?
\end{enumerate}
\item Colby:
\begin{enumerate}
 \item finish group member table, incorporate permissions usable by others
 \item finish group member controllers
 \item start permissions specific to groups (vs. existing gus admin permissions)
\end{enumerate}
\end{itemize}
\\  
\section{Any Other Business}
The next meeting is on Febuary 4th (today) @ 5:00pm in McClure 117. \\
\textbf{Scrum ends February 11th, 2011.}
\\
\section{Adjourned}
\textbf{Meeting closed at 14:20} \\
Closed by: Colby Blair \\
\end{document}
