\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\title{GusPHP}
\date{February 11th, 2011}
\author{Colby Blair}
\begin{document}
\maketitle
\begin{center}\textbf{Minutes of the meeting of GusPHP, University of Idaho CS-384 Spring 2011} \end{center} \\ \\
	Colby Blair - Group Leader\\ \\
\textbf{McClure 209 (in class), UI Campus, Moscow ID 83843} \\ \\
\textbf{Present}\\ 
Brett\\
Abhay\\
Zeke\\
Alex\\
Cindy\\
Chaylo\\
Colby\\
Scott\\
Tim\\
\\
\textbf{In Attendance}\\
None \\
\\
\section{Actions for consideration} \\
None \\
\\
\section{Any Other Business}
None \\
\\
\section{New Business}
Scrums are 1 week increments. Planning is complete at end of minutes. Code, Test, and Document this Scrum.\\
What will be completed in the next Scrum:\\
Everyone - \\
\begin{itemize}
  \item Finish DEPTH of your tests - Cindy and Leah will help
  \item Work with Cindy and Leah to get all your code files updated with phpdoc strings
\end{itemize}
\begin{itemize}
\item Cindy:
\begin{enumerate}
 \item Work with members so all files have phpdoc string - see controllers/admin.php
 \item Finish Red/Green Light test stubs for all tests cases - there should be a lot of red lights at the end of this week
 \item Leah shares these tasks
\end{enumerate}
\item Chaylo:
\begin{enumerate}
 \item Sick last week, finish last week requirements
 \item Tim will help start more features
\end{enumerate}
\item Zeke:
\begin{enumerate}
 \item Not present, please contact us for new requirements. Generally: look into existing systems we can link with gus so members can use a forum until the custom one is complete. Existing forums are phpbb, for example.
\end{enumerate}
\item Abhay:
\begin{enumerate}
 \item Finish integration of pm MVC's, start helping Alex with doc/upload meta data server
\end{enumerate}
\item Alex:
\begin{enumerate}
 \item start/finish file editing controller functions
 \item start meta data server that does some interfacing with sessions. Meta data server will have user-file db lookout table, to be completed by end of week
\end{enumerate}
\item Scott:
\begin{enumerate}
 \item finish test model for auto test logging. Correct Firefox CSS errors
\end{enumerate}
\item Brett:
\begin{enumerate}
 \item Finish user/group-page functionality. Get with Scott for implementing layouts
\end{enumerate}
\item Leah:
\begin{enumerate}
 \item assist Cindy
\end{enumerate}
\item Tim:
\begin{enumerate}
 \item assist with forum controller
\end{enumerate}
\item Colby:
\begin{enumerate}
 \item finish group-user lookout table w/ permissions. 
 \item Help Alex with his file-user lookup table. 
 \item Try linking a phpbb distro with out user db
 \item Same with a wikimedia distro
 \item Try openning up server (??) for team to dev on.
\end{enumerate}
\end{itemize}
\\  
\section{Any Other Business}
The next meeting is on Febuary 14th @ 5:30pm in McClure 117. \\
\textbf{Scrum ends February 18th, 2011.}
\\
\section{Adjourned}
\textbf{Meeting closed at 14:20} \\
Closed by: Colby Blair \\
\end{document}
