\subsection{Site dependencies}
			GUS will require a server that can support 1,000 concurrent
			users.  The database must store the information, interests,
			and activities of approximately 5,000 external users, 5,000
			students and 200 groups.
		\subsection{Safety, security and privacy requirements}
			GUS contains the personal information of over 5,000 users
			security should be integrated into every facet of this
			program.  The privacy criteria for this system must reflect
			privacy policies that apply to the University of Idaho, and
			the security criteria for this system must reflect the need
			to secure over 5,000 users from identity theft and potential
			defamation of character.
		\subsection{Performance requirements}
		\begin{enumerate}
			\item The number of simultaneous users to be supported are: 1,000.
			\item Supported information ranges from text to files to streaming video.
			\item 95\% of the transactions shall be processed in less than half a second.
		\end{enumerate}
		\subsection{System and software quality}
			Gus must perform all required functions, behave consistently
			and correctly, be easily corrected, running between 5:30 am
			all day to 1:30 am be easily adaptable, test-driven, and easy
			to use.
		\subsection{Packaging and delivery requirements}
			The executable system and all associated documentation (i.e.,
			SSRS, SDD, code listing, test plan (data and results), and
			user manual) will be delivered to the customer via Internet
			download. The final, edited version of the above documents
			will accompany the final, accepted version of the executable system.
		\subsection{Personnel-related requirements}
			The system under development will require a graduate student
			system-level administrator to maintain the system.
		\subsection{Training-related requirements}
			No training materials or expectations are tied to this
			project other than the limited help screens built into the
			software and the accompanying user manual.
		\subsection{Logistics-related requirements}
			A server will be required to maintain the software system.
			The user will be required to have an Internet connection.
		\subsection{Precedence and criticality of requirements}
			\begin{enumerate}
				\item Maintaining confidentiality and privacy of PII
				\item This system must be reliable enough for users to not
					give up on it
				\item All other features are less important than the first
					two and equally important
			\end{enumerate}